Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-09 paper.tex
fixed comment on matlab engines

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM) being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            MATLAB engine frameworks, such as PSOM, SPM and AA; LONI; Taverna; 
            MapReduce; and Spark \tristan{this list contains Matlab
            engines}. Nipype, FastR, Pydpiper are all python-based platform 
            independent workflow engines and Toil and Galaxy are CWL-based 
            platform independent engines. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE and Nextflow are 
            not platform-independent, but can execute on macOS and Linux.

@@

            Additionally, the details captured may differ slightly between 
            these frameworks. In addition to the basic amount of  provenance 
            captured, Pegasus records runtime information, data locations, 
            software used and parameters applied. Pydpiper captures the DAG, the 
            array of pipeline stages, the current stage counter, hash of stages 
            and output files and an array of stage statuses.As provenance is a 
            major component of the Galaxy project, it 
            provides comprehensive provenance tracking. This includes gathering
            of metadata similarly to other workflow engines, but also allows
            users to add annotations to make the intent of their analysis known
            .

            Some workflows engines do not really capture provenance details. At 
            most, the provenance captured is limited to runtime information.
            Nextflow, Make, Toil and MapReduce are all examples of these types
            of systems.

>>>>

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM), running on the MATLAB
            engine, being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            LONI, Taverna, MapReduce and Spark \tristan{this list contains Matlab
            engines}. MATLAB engine frameworks include PSOM, SPM and AA. 
            Nipype, FastR, Pydpiper are all python-based platform 
            independent workflow engines and Toil and Galaxy are CWL-based 
            platform independent engines. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE and Nextflow are 
            not platform-independent, but can execute on macOS and Linux.

@@

            Additionally, the details captured may differ slightly between 
            these frameworks. In addition to the basic amount of  provenance 
            captured, Pegasus records runtime information, data locations, 
            software used and parameters applied. Pydpiper captures the DAG, the 
            array of pipeline stages, the current stage counter, hash of stages 
            and output files and an array of stage statuses. As provenance is a 
            major component of the Galaxy project, it 
            provides comprehensive provenance tracking. This includes gathering
            of metadata similarly to other workflow engines, but also allows
            users to add annotations to make the intent of their analysis known
            .

            Some workflows engines capture limited provenance details. At 
            most, the provenance captured is limited to runtime information.
            Nextflow, Make, Toil and MapReduce are all examples of these types
            of systems.
